The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-07-18 paper.tex
Added intro to Irish case study

The {\sc Sonority Angles} for NT, TT and TN are calculated as follows.

@@

>>>>

The {\sc Sonority Angles} for NT, TT and TN are calculated as in the following examples.

@@

Irish displays an unusual process of epenthesis that targets consonant clusters 
whose first member is a sonorant \citep{carnie.1994, ni.chiosain.1999}, with the 
exception of sonorant-voiceless stop clusters, which never undergo epenthesis. 
I will show in this section that a {\sc Sonority Angle}-based faithfulness
neatly captures these facts.
